%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Chris}{Burke}
\title{Data Scientist}                               % optional, remove / comment the line if not wanted
\address{319 N Oak Park Ave Apt C}{Oak Park, IL 60302}
\phone[mobile]{614~595~6076}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\email{chris@caburke.com}                               % optional, remove / comment the line if not wanted
% \homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
\social[linkedin]{christophaburke}                        % optional, remove / comment the line if not wanted
\social[github]{caburke}                              % optional, remove / comment the line if not wanted
% \extrainfo{additional information}                 % optional, remove / comment the line if not wanted
% \photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
% \quote{Some quote}                                 % optional, remove / comment the line if not wanted


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle


\section{Experience}
\cventry{2021--2022}{Principal Data Scientist}{BlockFi}{}{}{Lead data scientist on the fraud team.
\begin{itemize}%
\item Built account monitoring process using pyspark, Databricks, and Jira REST API. Catching 10+ enrollments related to identity theft and elderly abuse daily with low false positive rate.
\item Develop data pipelines to ingest external data and create features used in account monitoring and account takeover risk engines.
\item Evaluate performance and value of vendor data and models. Work with engineering team to develop requirements for vendor integration.
\end{itemize}}
\cventry{2020--2021}{Principal Data Scientist}{Early Warning}{}{}{Building models, features, and data pipelines to support new products. Mentoring data scientists and other teams on how to effectively use EWS data. Communicating analyses and results from our team to both internal and external customers.
\begin{itemize}
\item Team lead for 2-4 data scientists. Translate requirements from other teams into projects and tasks, communicate timelines and blockers to management, review code, work to keep team members happy and productive.
\item Built features and trained highly accurate XGBoost classifier to predict fraudulent Zelle payments.
\item Working with internal tech partners to maintain and upgrade data science infrastructure.
\item Training data scientists on the use of Hadoop, Spark, Linux, Python, and other technology.
\end{itemize}}
\cventry{2019--2020}{Senior Data Scientist}{Early Warning}{}{}{Feature engineering and model development for classifier to predict fraudulent Zelle payments.}
\cventry{2018--2019}{Manager, Fraud Analytics}{Early Warning}{}{}{
Created tools to increase fraud detection, reduce operations cost, and support the growth of the Zelle payment network.
\begin{itemize}
\item Built internal fraud analytics packages in R with functions to quickly link fraud threats to specific attributes in our data.
\item Built command line tools allowing users to generate analyses
and visualizations of data from our risk engine and mobile
application data.
\item Designed schemas for FRM Hive databases to support ad hoc
queries by analytics team and efficient update of dashboards by
BI team.
\item Automated daily ETL pipeline with Spark. Wrote data to formats
readable by R, Python, and SAS to support multiple teams and
toolsets.
\item Communicate impact of changes to strategies and fraud losses to key stakeholders.
\end{itemize}}
\cventry{2017--2018}{Senior Fraud Event Analyst}{Early Warning}{}{}{Develop data pipelines and analytics framework to support the launch of Zelle.}
\cventry{2015--2017}{Data Scientist}{Consumer Financial Protection Bureau}{}{}{Built data based solutions for multiple departments throughout the CFPB.}
\cventry{2013--2015}{Research Assistant}{Univerisity of Cincinnati}{}{}{Analyzed gene expression data and developed statistical models of gene
regulatory networks.}
\cventry{2010--2012}{Teaching Assistant}{Univerisity of Cincinnati}{}{}{Professor of college algebra and statistics classes. Teaching assistant for calculus.}
\cventry{2009--2010}{Actuarial Analyst}{Anthem Insurance}{}{}{Pricing and forecasting for Medicare Advantage products.\newline{}}

\section{Education}
\cventry{2016}{Masters of Science}{University of Cincinnati}{Cincinnati, OH}{}{Mathematics}
\cventry{2015}{Masters of Science}{University of Cincinnati}{Cincinnati, OH}{}{Statistics}
\cventry{2008}{Bachelors of Science}{Ohio State University}{Columbus, OH}{}{Dual Major in Mathematics and Economics}

\section{Computer skills}
\cvitem{Python}{Extensive experience using python for analytics, modeling, visualization and ETL.}
\cvitem{SQL}{Experience with MS-SQL, Postgres, Hive, Redshift and SQLite.}
\cvitem{Spark}{Develop data pipelines using pyspark and the scala API in Hadoop and Databricks.}
\cvitem{R}{Built libraries for fraud analytics, report generation, and visualization using data.table, rmarkdown, ggplot2 and other libraries.}
\cvitem{Docker}{Understand basics of Docker and have used docker images to deploy models created in DataRobot.}
\cvitem{Web Dev}{Built Flask apps and R Shiny apps as UIs for analyses and visualizations. Basic understanding of HTML/CSS/Javascript.}

\end{document}


%% end of file `template.tex'.
